
## Activity Monitoring Devices


### Introduction

It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the "quantified self" movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

### Data

The variables included in this dataset are:

    steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)

    date: The date on which the measurement was taken in YYYY-MM-DD format

    interval: Identifier for the 5-minute interval in which measurement was taken

The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset.

### Loading and Processing the data

First let us load the data into R
```{r}
data <- read.csv("./activity.csv")
```

### Mean total number of steps taken per day

To find mean total number of steps taken per day ,first let us calculate the total number 
of steps taken per day

```{r}
s <- tapply(data$steps,data$date,sum,na.rm = TRUE)
print(s)
```

Now have the total number of steps taken per day.

Now we are making a histogram for total number of steps taken each day

```{r}
hist(s,xlab = "Number of steps taken each day",main = "Histogram for total number of steps taken each day")
```

Mean of total number of steps taken per day 

```{r}
mean(s)
```

Median of total number of steps takend per day

```{r}
median(s)
```

## Average Daily activity pattern

Now we need to make a time series plot of the 5-minute interval which is on x- axis and the average number of steps taken, averaged across all days on y -axis

```{r}
s2 <- tapply(data$steps,data$interval,mean,na.rm = TRUE)
plot(unique(data$interval),s2,type = "l",xlab = "5 - minute interval",ylab = "average number of steps taken,averaged across all days", main = "Average daily pattern")
```

We need to find which 5 - minute interval, on average across all the days in the dataset, contains the maximum number of steps

The details of the interval which contains maximum number of steps
```{r}
a <- sort(s2,decreasing = TRUE)
a[1]
```

##Imputing missing values

